### 2016-10-05 robust-software.tex
Rules are necessary but not sufficient for services

\item
Mention that these rules are necessary but not sufficient for software that needs to interact with services
such as database and web servers.
Such software is often stopped and started under automatic control,
may need to authenticate,
etc.,
all of which are out of scope of this paper.

@@

>>>>

@@

Any short list of rules for developing robust software will
necessarily be incomplete.  For example, the rules we present above
are necessary, but not sufficient, for software that needs to interact
with services such as database and web servers.  Such software is
often stopped and started under automatic control, may need to
authenticate, etc., all of which are out of scope of this paper.
